### 2021-04-19 thesis_main/Chapter7_MS.tex
Initial commit

In this chapter we will adapt the MSE-based criteria derived before to the factorial experiments with units distributed in several strata. First we shall briefly review the approaches to the inference from the experiments with multi-level unit structures, and then will define the MSE-based optimality for the multistratum framework and provide the implementation strategy for the corresponding design search.

@@

\subsection{Response-Surface Methodology for Multistratum Designs}
%% Model. Ratio of variances.
As randomisation occurs at each stratum, the model accounting for the hierarchical error structure and correlated observations can be written as
\begin{equation}
\label{eq::MS_model}
\bm{Y}=\bm{X}\bm{\beta}+\sum_{i=1}^{s}\bm{Z}_{i}\bm{\varepsilon}_{i},
\end{equation}
where $\bm{Y}$ represents the $n$-dimensional vector of responses, $\bm{X}$ stands for the $n \times p$ model matrix and $\bm{\beta}$ for the $p$-dimensional vector of corresponding model coefficients. Each row of the $n\times m_{i}$ matrix $\bm{Z}_{i}$ corresponds to a single experimental run and indicates the unit in stratum $i$ containing this run. $\bm{\varepsilon}_{i}$ is a vector of random effects occurring due to the randomisation at level $i$, and these effects are assumed to be independent and identically distributed around zero mean and variance $\sigma^{2}_{i}$. The assumption of error normality, though quite common is required for some analysis methods, is not a necessary one at this stage.

@@

\subsubsection{REML Methodology}
An extensive amount of research has been conducted on the design of and analysis of data from split-plot and split-split-plot experiments, with one of the first works by \cite{Letsinger1996BiRandomization}, emphasising the necessity of adapting the design and analysis strategy with respect to the more complicated error structure.  In the most general case of non-orthogonal unit structures Residual Maximum Likelihood (REML) methodology has been acknowledged to be the most sensible approach to estimating the variance components by maximising the part of the likelihood function corresponding to the ``random'' part of the model; the details are provided, for example, in \cite{Searle2001generalized}.

@@

\subsection{Full Treatment Model}

@@

\subsubsection{Pure-error REML}
\cite{GilmourGoos2016PEREML} introduced the notion of ``Pure Error REML'', such that the random effects are estimated from the treatment model (\ref{eq::treatmentMS}), and then for the sake of making inference regarding parameters of the response model (\ref{eq::MS_model}), they are substituted in the GLS estimators of the fixed effects (\ref{eq::MS_GLS}). It is also argued that some appropriate corrections are to be adapted and applied to the obtained estimates, i.e.~the ones suggested by \cite{kenward1997small}.

@@

\subsubsection{Yates' procedure}
\label{sec::ch7_varest}
The first approach is stratum-by-stratum data analysis, where each randomisation level is considered separately, and at each stratum $i$ units are treated as runs aggregated in $m_{i-1}$ blocks with fixed effects. The lower stratum variance is estimated from within blocks (using intra-block residual mean square), and the higher stratum (inter-block) variance from the difference between the intra- and inter-block residual mean squares scaled by the number of runs per block \citep{Hinkelmann2005Advanced}. This simple strategy requires no other assumptions except for the treatment-unit additivity and provides unbiased treatment effects' estimators.

@@

\subsection{Design Construction for MSE-based Optimality Criteria}
\label{sec::ch7_search}
With the theoretical insights discussed above in mind, the practical adaptation and implementation of the MSE-based criteria for multistratum experiments shall be presented as the algorithm of the corresponding optimal design search which is in accordance with the inference strategy described in the previous section.

@@

\subsubsection{Construction procedure}
The design construction will follow the approach developed by \cite{Trinca2015improved}: an iterative, stratum-by-stratum algorithm, that treats the higher stratum units as fixed blocks; such an approach does not require any prior assumptions regarding the values of the variance components.

@@

\subsubsection{Allocation of degrees of freedom}

@@

>>>>

 %%% Multi-stratum designs, MSE-criteria
In this chapter we will adapt the MSE-based criteria derived before to the factorial experiments with units distributed in several strata. First we shall briefly review the approaches to the inference from the experiments with multi-level unit structures, and then will define the MSE-based optimality for the multistratum framework and provide the implementation strategy for the corresponding design search.

@@

\section{Response-Surface Methodology for Multistratum Designs}
%% Model. Ratio of variances.
As randomisation occurs at each stratum, the model accounting for the hierarchical error structure and correlated observations can be written as
\begin{equation}
\label{eq::MS_model}
\bm{Y}=\bm{X}\bm{\beta}+\sum_{i=1}^{s}\bm{Z}_{i}\bm{\varepsilon}_{i},
\end{equation}
where $\bm{Y}$ represents the $n$-dimensional vector of responses, $\bm{X}$ stands for the $n \times p$ model matrix and $\bm{\beta}$ for the $p$-dimensional vector of corresponding model coefficients. Each row of the $n\times m_{i}$ matrix $\bm{Z}_{i}$ corresponds to a single experimental run and indicates the unit in stratum $i$ containing this run. $\bm{\varepsilon}_{i}$ is a vector of random effects occurring due to the randomisation at level $i$, and these effects are assumed to be independent and identically distributed around zero mean and variance $\sigma^{2}_{i}$. The assumption of error normality, though quite common is required for some analysis methods, is not a necessary one at this stage.

@@

\section{REML Methodology}
An extensive amount of research has been conducted on the design of and analysis of data from split-plot and split-split-plot experiments, with one of the first works by \cite{Letsinger1996BiRandomization}, emphasising the necessity of adapting the design and analysis strategy with respect to the more complicated error structure.  In the most general case of non-orthogonal unit structures Residual Maximum Likelihood (REML) methodology has been acknowledged to be the most sensible approach to estimating the variance components by maximising the part of the likelihood function corresponding to the ``random'' part of the model; the details are provided, for example, in \cite{Searle2001generalized}.

@@

\section{Full Treatment Model}

@@

\subsection{Pure-error REML}
\cite{GilmourGoos2016PEREML} introduced the notion of ``Pure Error REML'', such that the random effects are estimated from the treatment model (\ref{eq::treatmentMS}), and then for the sake of making inference regarding parameters of the response model (\ref{eq::MS_model}), they are substituted in the GLS estimators of the fixed effects (\ref{eq::MS_GLS}). It is also argued that some appropriate corrections are to be adapted and applied to the obtained estimates, i.e.~the ones suggested by \cite{kenward1997small}.

@@

\subsection{Yates' procedure}
\label{sec::ch7_varest}
The first approach is stratum-by-stratum data analysis, where each randomisation level is considered separately, and at each stratum $i$ units are treated as runs aggregated in $m_{i-1}$ blocks with fixed effects. The lower stratum variance is estimated from within blocks (using intra-block residual mean square), and the higher stratum (inter-block) variance from the difference between the intra- and inter-block residual mean squares scaled by the number of runs per block \citep{Hinkelmann2005Advanced}. This simple strategy requires no other assumptions except for the treatment-unit additivity and provides unbiased treatment effects' estimators.

@@

\section{Design Construction for MSE-based Optimality Criteria}
\label{sec::ch7_search}
With the theoretical insights discussed above in mind, the practical adaptation and implementation of the MSE-based criteria for multistratum experiments shall be presented as the algorithm of the corresponding optimal design search which is in accordance with the inference strategy described in the previous section.

@@

\subsection{Construction procedure}
The design construction will follow the approach developed by \cite{Trinca2015improved}: an iterative, stratum-by-stratum algorithm, that treats the higher stratum units as fixed blocks; such an approach does not require any prior assumptions regarding the values of the variance components.

@@

\subsection{Allocation of degrees of freedom}

@@

This particular design was obtained according to one of the MSE(D)-optimality criteria, and its summary is presented in Table \ref{tab::mseD_ex2} (design \#$5$ for $\tau^2=1/q$); the outline of the experimental framework is given in detail in the next Section.

\section{Examples}
\label{sec::ch7_ex}
\input{Chapter7_Examples}

\section{Conclusions}

In a multistratum experiment the problem of obtaining optimal designs for the inferential objectives becomes more complicated once the number of randomisation levels increases and, therefore, so does the difficulty of dealing with the larger number of unknown nested variance components.

\subsection{Discussion}
We brought together the MSE-based compound optimality criteria developed for the purposes of pure error inference, lack-of-fit and minimising the impact of the potential model misspecification, and the inference-based design search strategy for the multistratum experiments.

Adapting the stratum-by-stratum approach and clearly defining the consistent procedures of estimating the degrees of freedom and variance components resulted in the framework allowing for obtaining MSE-based optimal designs for any factorial experiment with restricted randomisation.

The flexibility of the algorithm and its implementation implies the minimum number of amendments required in order to apply it for a particular experimental setup. We considered a few illustrative examples for the aims of exploring the resulting designs' behaviour in terms of the replicated points allocation between and within strata, we looked at the trade-off patterns among individual criterion components and the dynamic of designs' performances across different values of the variance scaling parameter.

\subsection{Some practical recommendations}

Although it is widely acknowledged that restricted randomisation has to be taken into account at the stage of design planning, finding a specific approach still might be a problem.

Use of the MSE-based criteria for a multistratum experiment, following the algorithm described in Section \ref{sec::ch7_search}, does require some careful preliminary thought regarding not only the exact layout of the experiment (which is essential anyway), but also regarding the choice of the criterion (determinant- or trace-based), and the weights that are to be put on the components at each strata, as these specifics have been shown to greatly influence the performances of the resulting designs. The choice of the variance scaling parameter $\tau^2$, though is rather important, seems to have a more predictable effect on the optimal designs' performance characteristics.

However, the approach presented is computationally inexpensive: a single design construction would not typically take more than $3$--$4$ hours (e.g. for a split-split-plot design with some non-zero weight on all three component criteria). This would allow examining a few alternatives (similar to what has been done in the case-study described in Chapter \ref{ch::mse_blocked}, Section \ref{sec::case_study}), and their relative performance characteristics and then making a choice that would best fit the particular experimental requirements.

In addition, the algorithm can be easily adapted if the weight allocation scheme or values of the variance scaling parameter $\tau^2$ is to be changed between strata (even though the result would not be expected to be sensitive to a misspecification of $\tau^2$).

### 2021-04-19 thesis_main/Corrections.tex
Initial commit

\documentclass[11pt,a4paper,oneside]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[USenglish]{babel}
\usepackage{graphicx} % Allows including images
%\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{color, soul}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{parskip}
\usepackage[authoryear,round]{natbib}
\usepackage[applemac]{inputenx}
\usepackage{caption} \captionsetup[table]{skip=5pt}
%\setlength{\parskip}{\baselineskip}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{lscape}    %changing page orientation

@@

\textbf{Chapter 2. Background and Related Work}
\begin{enumerate}
\item Page 9. ``.. and derived the $DP$-criterion: minimising $(F_{p,d;1-\alpha_{DP}})^{p}\vert(\bm{X'}\bm{X})^{-1}\vert$'' (was $\nu$ instead of $d$)
\item \hl{Page 10. Expanding the explanation of where L-optimality comes from}: ``If we are interested in the functions of parameters given by $\bm{L}'\bm{\beta}$, then the variance-covariance matrix of $\bm{L}'\bm{\hat{\beta}}$ is...''
\item \hl{Page 10. Explaining why Sidak's corrections were used}: ``Here we shall use Sidak's correction \citep{vsidak1967rectangular}, which is...''
\item Page 10. ``.. for example, $I$-optimality, that is minimising \textbf{average} prediction variance''
\item \hl{Page 11. Rephrasing in order to make a sentence more readable}: "The idea of compound criteria <...>  allows finding a compromise between two or more desirable properties while searching for the design, and explore how the changes in the allocation of weights between the individual criteria affect the optimal designs' performances."
\item Page 11. ``.. prior knowledge of the \textbf{experimenter}'' (misprint)
\item Page 12. ``.. it is sometimes \textbf{necessary} to allocate units in blocks''
\item Page 12. ``.. its $(i,j)^{th}$ element''
\item Page 12. ``.. and $\bm{\beta}_B$ is the vector of block effects''
\item Page 13. ``.. matrix whose elements indicate \textbf{the} treatments''
\item Page 13. ``.. the number of replications after \textbf{subtracting the number of replicates} taken for the estimation of block contrasts.''
\item  \hl{Page 15}.``.. \cite{Goos2001Doptimal} considered the three cases when D-optimal designs for split-plot experiments do not depend on the value of $\eta$; in other practical cases an estimate of the variance ratio is to be provided.'' 
\item  \hl{Page 16}. ``\cite{Arnouts2012staggered} presented a coordinate-exchange algorithm \ldots examples of D- and I-optimal designs.''
\item Page 16. ``.. assumed possible values of $\eta_i$'' (misprint)
\item Page 16. ``.. in the presence'' (misprint)
\item \hl{Page 17. ``In this thesis, due to the primary interest being the quality of inference,..''}
\item Page 18. Removed ``Therefore'' in the 4th paragraph.
\end{enumerate}

\textbf{Chapter 3. Compound criteria. Some amendments}
\begin{enumerate}
\item Page 20. Adding significance levels where they were missed: $F_{n-p-d,d;1-\alpha_{LoF}}$ instead of $F_{n-p-d,d}$, and on Figure 3.1 on page 21.
\item \hl{Page 21. Expanding interpretation of the plot in Figure 3.1}: ``Larger numbers of available residual degrees of freedom \ldots'' 
\item Page 21. ``The third component in both criteria corresponds to the DF-efficiency defined in (2.7).''
\item Pages 22 and 24. Tables 3.1 and 3.4: added columns with DF-efficiency values
\item Page 23. ``..therefore, their $DF$-efficiency values $\frac{n-d}{n}$ are below $75\%$ (i.e. when $d>10$).'' 
\item Page 24. ``..the design optimal <\ldots> (\#$12$) is also optimal with respect to the criterion with equal weights put on the $DF$- and $LoF$-components'' 
\item Page 25. ``..except for the point number $18-19$ and the point number $36-37$''
\item Page 25. ``..the resulting efficiency values. It also would be sensible..'' (breaking the sentence)
\item \hl{Page 27. Adding extra comment}: ``This particular parametrisation <\ldots> designs which are more than $50\%$ efficient.''
\item Page 27. Adding subsection 3.2.2 Optimal designs (no text amendments)
\item Pages 28 and 29.  Tables 3.6 and 3.7: added columns with DF-efficiency values
\item \hl{Page 29. Paraphrasing the last paragraph}: ``It was desired to alter the form of an efficiency's contribution..''
\end{enumerate}

\textbf{Chapter 4. Generalised Compound Criteria}
\begin{enumerate}
\item \hl{Page 31. Adding bullet points in the chapter introduction}
\item Page 32 - 33. Adding subsections 4.1.1 and 4.1.2
\item Page 32. Equation (4.3) -- $\varepsilon$ in the subscripts
\item Page 33. ``..how large the magnitude of each of the potential terms is assumed to \textbf{possibly} be..''
\item Page 34. ``..we incorporate $L$-optimality for the primary terms..''
\item Pages 35 and 36. ``..and (4.11)''
\item Page 35. Adding the reference to Section 3.1.1
\item Page 37. Adding the reference to \cite{DuMouchel1994})
\item !!!\hl{Page 37. Amending the derivation of the formula for the confidence region for $\bm{\beta}_2$ over the posterior distribution (introducing the corresponding F-quantile)}.
\item Page 39. ``Henceforth'' instead of ``Here and further on''
\item Page 40. ``The results should'' instead of ``The results would''
\item Page 43. Table 4.6, $2$nd part, column names: \textbf{L}, \textbf{LP}, \textbf{LoF(LP)} and \textbf{Bias(L)}
\item Page 44. Rephrasing: ``similar tendency seems to be true''
\item \hl{Page 49. Paragraph 3. Adding an explanation regarding large $LoF$-efficiencies} in the case of smaller $\tau^2$: ``Such consistently high performance...''
\item Page 53. ``..each factor can take five levels..''
\item Page 53. ``all third and \textbf{fourth} order terms are taken as potentially missed terms''
\item Page 53. Adding: `` Most of the replicates are at corner points...''
\item Page 58. Changing the name of Section 4.3 (to ``Blocked Experiments'') and adding  subsection 4.3.1 ``Generalised criteria''
\item Page 58. Adding ``$\bm{\beta}_{B}$ is the vector of \textbf{fixed block effects},...'' 
\item Page 59. $\bm{\beta}_{B}$ instead of $\bm{\beta}_{0}$
\item Page 59. ``Therefore, ...'' 
\item Page 60. ``\textbf{the} $D$-optimal design''
\item !!\hl{Page 64. Adding a comment regarding ignoring the orthonormalisation}: ``Ignoring such a requirement would amend the formulae of the bias components, but in general it should not be expected to considerably influence the resulting optimal designs and their performances; though the orthonormalisation step should not be blindly omitted, especially if the prediction bias is of a particular interest.''
\end{enumerate}

\textbf{Chapter 5. MSE-based Criteria}
\begin{enumerate}
\item \hl{Page 66. Adding an explanation of `pseudo-Bayesian'}: ``..(hence we shall refer to such an approach as ``pseudo-Bayesian'')..''
\item Page 67. ``.. and $\bm{u}$, $\bm{v}$ are column vectors''
\item Page 68. Adding a definition of $\bm{\tilde{\beta}}_{2i}$ after the equation (5.5): ``Here $\bm{\tilde{\beta}}_{2i}$, $i=1..N$ -- independent random vectors sampled from $\mathcal{N}(\bm{0},\tau^{2}\sigma^{2}\bm{I}_{q})$.''
\item Page 70. Emphasising the computational advantage of the trace-based criterion: ``The main advantage is the absence of the necessity of any additional numerical evaluations, and...'' 
\item Page 74. Amending the interpretation: ``..the decreased scale of the potentially missed contamination results in \textbf{an easier achievable compromise} between...'' 
\item Page 74. ``.. in the corresponding tables'' 
\item Page 74. Rephrasing: ``..in the case of $MSE(D)$-efficient designs with smaller $\tau^2$.''
\end{enumerate}

\textbf{Chapter 6. MSE-based Criteria for Blocked Experiments}
\begin{enumerate}
\item Page 78. Equation (6.2): $\bm{\beta}_B$ and $\bm{\beta}_1$ instead of $\bm{\tilde{\beta}}_b$ and $\bm{\tilde{\beta}}_p$
\item Page 82. ``in the design \#$8$''
\item \hl{Page 84. Adding a comment regarding relative efficiencies} between the designs optimal w.r.t. the continuous and point-prior-based criteria: ``As for the efficiency losses...''
\item \hl{Page 85. Reason for fixing two centre points per block in the case-study:}``... the experimenters wanted to have at least two centre points in each block to ensure representation of the conditions thought a priori most likely to be best (with dosages of $95\%$ for each supplement)''
\item Page 87. ``$LoF(DP)-$''
\item Page 88. Amending the explanation of the ``Relative efficiency'': ``The last column of this table, ``Relative Efficiency,'' is..''
\item Page 91. Misprint: ``experimenters''
\end{enumerate}

\textbf{Chapter 7. MSE-based Criteria for Multistratum Experiments}
\begin{enumerate}
\item Page 94. Changing \textbf{REML Methodology} from a subsection to section
\item \hl{Page 96}. Changing the title of Section 7.2.2: ``Yates' procedure'' 
\item Page 97. ``$m_j=\ldots$ \textbf{units}''
\item \hl{Page 98}. Adding the \textbf{Construction procedure} subsection title (no text amendments)
\item Page 103. Expanding the sentence: ``Now we need to evaluate the number of degrees of freedom for..''
\item Page 103. ``.. the factors applied at the current and \textbf{all} higher strata''
\item \hl{Page 104. Explaining why $\tau^2=\sqrt{1/q}$ was used}: ``As this number tends to become..''
\item Page 104. ``Regarding the \textbf{third-order} potential terms..''
\item Page 106. ``(design\textbf{s} \#$3$)''
\item Page 106. ``.. designs \#$5$ and \#$7$ provide the worst performance with respect to the $MSE(L)-$ and $LP$-components respectively''
\item Page 109. ``i.e. designs \#$6$ in Table 7.6''
\item Page 111. Adding the \textbf{Discussion} subsection title (no text amendments)
\end{enumerate}

\textbf{Chapter 8. Conclusions and Future Work}
\begin{enumerate}
\item \hl{Page 114. Adding a comment regarding advantages and disadvantages} of the Pareto frontier approach: ``On one hand, such an algorithm would result in a set of designs...''
\end{enumerate}

>>>>

\documentclass[11pt,a4paper,oneside]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage[USenglish]{babel}
\usepackage{graphicx} % Allows including images
%\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{color}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{parskip}
\usepackage[authoryear,round]{natbib}
\usepackage[applemac]{inputenx}
\usepackage{caption} \captionsetup[table]{skip=5pt}
%\setlength{\parskip}{\baselineskip}
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{lscape}    %changing page orientation

@@

\textbf{Chapter 2. Background and Related Work}
\begin{enumerate}
\item Page 9. ``.. and derived the $DP$-criterion: minimising $(F_{p,d;1-\alpha_{DP}})^{p}\vert(\bm{X'}\bm{X})^{-1}\vert$'' (was $\nu$ instead of $d$)
\item Page 10. Expanding the explanation of where L-optimality comes from: ``If we are interested in the functions of parameters given by $\bm{L}'\bm{\beta}$, then the variance-covariance matrix of $\bm{L}'\bm{\hat{\beta}}$ is...''
\item Page 10. Explaining why Sidak's corrections were used: ``Here we shall use Sidak's correction \citep{vsidak1967rectangular}, which is...''
\item Page 10. ``.. for example, $I$-optimality, that is minimising \textbf{average} prediction variance''
\item  \hl{Page 11. Adding a comment regarding the reasons to use the compound criterion approach:} ``... and explore how the changes in the allocation of weights between the individual criteria affect the optimal designs' performances.''
\item Page 11. ``.. prior knowledge of the \textbf{experimenter}'' (misprint)
\item Page 12. ``.. it is sometimes \textbf{necessary} to allocate units in blocks''
\item Page 12. ``.. its $(i,j)^{th}$ element''
\item Page 12. ``.. and $\bm{\beta}_B$ is the vector of block effects''
\item Page 13. ``.. matrix whose elements indicate \textbf{the} treatments''
\item Page 13. ``.. the number of replications after \textbf{subtracting the number of replicates} taken for the estimation of block contrasts.''
\item Page 15. ``.. \cite{Goos2001Doptimal} considered the three cases when D-optimal designs for split-plot experiments do not depend on the value of $\eta$; in other practical cases an estimate of the variance ratio is to be provided.'' 
\item Page 16. ``\cite{Arnouts2012staggered} presented a coordinate-exchange algorithm \ldots examples of D- and I-optimal designs.''
\item Page 16. ``.. assumed possible values of $\eta_i$'' (misprint)
\item Page 16. ``.. in the presence'' (misprint)
\item Page 17. ``In this thesis, due to the primary interest being the quality of inference,..''
\item Page 18. Removed ``Therefore'' in the 4th paragraph.
\end{enumerate}

\textbf{Chapter 3. Compound criteria. Some amendments}
\begin{enumerate}
\item Page 20. Adding significance levels where they were missed: $F_{n-p-d,d;1-\alpha_{LoF}}$ instead of $F_{n-p-d,d}$, and on Figure 3.1 on page 21.
\item Page 21. Expanding interpretation of the plot in Figure 3.1: ``Larger numbers of available residual degrees of freedom \ldots'' 
\item Page 21. ``The third component in both criteria corresponds to the DF-efficiency defined in (2.7).''
\item Pages 22 and 24. Tables 3.1 and 3.4: added columns with DF-efficiency values
\item Page 23. ``..therefore, their $DF$-efficiency values $\frac{n-d}{n}$ are below $75\%$ (i.e. when $d>10$).'' 
\item Page 24. ``..the design optimal <\ldots> (\#$12$) is also optimal with respect to the criterion with equal weights put on the $DF$- and $LoF$-components'' 
\item Page 25. ``..except for the point number $18-19$ and the point number $36-37$''
\item Page 25. ``..the resulting efficiency values. It also would be sensible..'' (breaking the sentence)
\item Page 27. Adding extra comment: ``This particular parametrisation <\ldots> designs which are more than $50\%$ efficient.''
\item Page 27. Adding subsection 3.2.2 Optimal designs (no text amendments)
\item Pages 28 and 29.  Tables 3.6 and 3.7: added columns with DF-efficiency values
\item Page 29. Paraphrasing the last paragraph: ``It was desired to alter the form of an efficiency's contribution..''
\end{enumerate}

\textbf{Chapter 4. Generalised Compound Criteria}
\begin{enumerate}
\item Page 31. Adding bullet points in the chapter introduction
\item Page 32 - 33. Adding subsections 4.1.1 and 4.1.2
\item Page 32. Equation (4.3) -- $\varepsilon$ in the subscripts
\item Page 33. ``..how large the magnitude of each of the potential terms is assumed to \textbf{possibly} be..''
\item Page 34. ``..we incorporate $L$-optimality for the primary terms..''
\item Pages 35 and 36. ``..and (4.11)''
\item Page 35. Adding the reference to Section 3.1.1
\item Page 37. Adding the reference to \cite{DuMouchel1994})
\item Page 37. Amending the derivation of the formula for the confidence region for $\bm{\beta}_2$ over the posterior distribution (introducing the corresponding F-quantile).
\item Page 39. ``Henceforth'' instead of ``Here and further on''
\item Page 40. ``The results should'' instead of ``The results would''
\item Page 43. Table 4.6, $2$nd part, column names: \textbf{L}, \textbf{LP}, \textbf{LoF(LP)} and \textbf{Bias(L)}
\item Page 44. Rephrasing: ``similar tendency seems to be true''
\item Page 49. Paragraph 3. Adding an explanation regarding large $LoF$-efficiencies in case of smaller $\tau^2$: ``Such consistently high performance...''
\item Page 53. ``..each factor can take five levels..''
\item Page 53. ``all third and \textbf{fourth} order terms are taken as potentially missed terms''
\item Page 53. Adding: `` Most of the replicates are at corner points...''
\item Page 58. Changing the name of Section 4.3 (to ``Blocked Experiments'') and adding  subsection 4.3.1 ``Generalised criteria''
\item Page 58. Adding ``$\bm{\beta}_{B}$ is the vector of \textbf{fixed block effects},...'' 
\item Page 59. $\bm{\beta}_{B}$ instead of $\bm{\beta}_{0}$
\item Page 59. ``Therefore, ...'' 
\item Page 60. ``\textbf{the} $D$-optimal design''
\item Page 64. Adding a comment regarding ignoring the orthonormalisation: ``Ignoring such a requirement would amend the formulae of the bias components, but in general it should not be expected to considerably influence the resulting optimal designs and their performances; though the orthonormalisation step should not be blindly omitted, especially if the prediction bias is of a particular interest.''
\end{enumerate}

\textbf{Chapter 5. MSE-based Criteria}
\begin{enumerate}
\item Page 66. Adding an explanation of `pseudo-Bayesian': ``..(hence we shall refer to such an approach as ``pseudo-Bayesian'')..''
\item Page 67. ``.. and $\bm{u}$, $\bm{v}$ are column vectors''
\item Page 68. Adding a definition of $\bm{\tilde{\beta}}_{2i}$ after the equation (5.5): ``Here $\bm{\tilde{\beta}}_{2i}$, $i=1..N$ -- independent random vectors sampled from $\mathcal{N}(\bm{0},\tau^{2}\sigma^{2}\bm{I}_{q})$.''
\item Page 70. Emphasising the computational advantage of the trace-based criterion: ``The main advantage is the absence of the necessity of any additional numerical evaluations, and...'' 
\item \hl{Page 74. Amending the interpretation:} ``..the decreased scale of the potentially missed contamination results in \textbf{a more easily achievable compromise} between...'' 
\item Page 74. ``.. in the corresponding tables'' 
\item Page 74. Rephrasing: ``..in the case of $MSE(D)$-efficient designs with smaller $\tau^2$.''
\end{enumerate}

\textbf{Chapter 6. MSE-based Criteria for Blocked Experiments}
\begin{enumerate}
\item Page 78. Equation (6.2): $\bm{\beta}_B$ and $\bm{\beta}_1$ instead of $\bm{\tilde{\beta}}_b$ and $\bm{\tilde{\beta}}_p$
\item Page 82. ``in the design \#$8$''
\item Page 84. Adding a comment regarding relative efficiencies between the designs optimal w.r.t. the continuous and point-prior-based criteria: ``As for the efficiency losses...''
\item Page 85. Adding explanation about two centre points requirement: ``..two centre points to ensure representation of the conditions thought a priori most likely to be best...'' 
\item Page 87. ``$LoF(DP)-$''
\item Page 88. Amending the explanation of the ``Relative efficiency'': ``The last column of this table, ``Relative Efficiency,'' is..''
\item Page 91. Misprint: ``experimenters''
\end{enumerate}

\textbf{Chapter 7. MSE-based Criteria for Multistratum Experiments}
\begin{enumerate}
\item Page 94. Changing \textbf{REML Methodology} from a subsection to section
\item Page 96. Changing the title of Section 7.2.2: ``Yates' procedure'' 
\item Page 97. ``$m_j=\ldots$ \textbf{units}''
\item Page 98. Adding the \textbf{Construction procedure} subsection title (no text amendments)
\item Page 103. Expanding the sentence: ``Now we need to evaluate the number of degrees of freedom for..''
\item Page 103. ``.. the factors applied at the current and \textbf{all} higher strata''
\item Page 104. Explaining why $\tau^2=\sqrt{1/q}$ was used: ``As this number tends to become..''
\item Page 104. ``Regarding the \textbf{third-order} potential terms..''
\item Page 106. ``(design\textbf{s} \#$3$)''
\item Page 106. ``.. designs \#$5$ and \#$7$ provide the worst performance with respect to the $MSE(L)-$ and $LP$-components respectively''
\item Page 109. ``i.e. designs \#$6$ in Table 7.6''
\item Page 111. Adding the \textbf{Discussion} subsection title (no text amendments)
\end{enumerate}

\textbf{Chapter 8. Conclusions and Future Work}
\begin{enumerate}
\item Page 114. Adding a comment regarding advantages and disadvantages of the Pareto frontier approach: ``On one hand, such an algorithm would result in a set of designs...''
\end{enumerate}
